Manuscript

### 2020-01-07 manuscript.Rmd
edit

---
output              :
  word_document     :
    reference_docx  : ./word_reference_template.docx
    toc             : true
    toc_depth       : 2
    fig_caption     : true
    df_print        : kable
    # citation_package: natbib
header-includes:
- \usepackage{caption}
title               : "Manuscript Draft"
author              :
- Sally E. Claridge
- Daniel M. Charytonowicz
- Adam A. Margolin
date                : "`r format(Sys.time(), '%d %B %Y')`"
bibliography        : manuscript.bib
fontsize            : 12pt
geometry            : margin=1in
linkcolor           : blue
urlcolor            : blue
citecolor           : blue
floatsintext        : yes
figurelist          : no
tablelist           : no
footnotelist        : no
linenumbers         : yes
abstract            : Multiple high-throughput functional screens in cancer cell lines have generated large amounts of information on drug efficacy in a variety of genomic contexts and cancer lineages. Reported inconsistencies between datasets have led us to investigate whether these large-scale screens reproduce established clinical drug-gene associations and if genomic features particular to specific genes improve said reproducibility. We evaluated three large-scale, small-molecule drug screens within the context of clinical interpretations derived from a new cancer variant annotation resource published by the Variant Interpretation for Cancer Consortium (VICC). We identified low levels of concordance between the three drug screen datasets and clinical drug-gene associations using mutation status, gene expression, and copy number as genomic indicators. Less than half of the clinical drug-gene cancer associations from the VICC resource were identified in these three drug screen datasets, suggesting a barrier to translating findings from these large-scale screens into the clinic.
---

>>>>

---
output              :
  word_document     :
    reference_docx  : ./word_reference_template.docx
    toc             : true
    toc_depth       : 2
    fig_caption     : true
    df_print        : kable
    # citation_package: natbib
header-includes:
- \usepackage{caption}
title               : "Manuscript Draft"
author              :
- name: Sally E. Claridge
  affiliation: Icahn School of Medicine at Mount Sinai
- name: Daniel M. Charytonowicz
  affiliation: Icahn School of Medicine at Mount Sinaiy
- name: Adam A. Margolin
  affiliation: Icahn School of Medicine at Mount Sinai
date                : "`r format(Sys.time(), '%d %B %Y')`"
bibliography        : manuscript.bib
fontsize            : 12pt
geometry            : margin=1in
linkcolor           : blue
urlcolor            : blue
citecolor           : blue
floatsintext        : yes
figurelist          : no
tablelist           : no
footnotelist        : no
linenumbers         : yes
abstract            : Multiple high-throughput functional screens in cancer cell lines have generated large amounts of information on drug efficacy in a variety of genomic contexts and cancer lineages. Reported inconsistencies between datasets have led us to investigate whether these large-scale screens reproduce established clinical drug-gene associations and if genomic features particular to specific genes improve said reproducibility. We evaluated three large-scale, small-molecule drug screens within the context of clinical interpretations derived from a new cancer variant annotation resource published by the Variant Interpretation for Cancer Consortium (VICC). We identified low levels of concordance between the three drug screen datasets and clinical drug-gene associations using mutation status, gene expression, and copy number as genomic indicators. Less than half of the clinical drug-gene cancer associations from the VICC resource were identified in these three drug screen datasets, suggesting a barrier to translating findings from these large-scale screens into the clinic.
---
